\section{\sc Technical Reports}
	\textbf{A. Gholami}, "\textit{Real-time Face Recognition Based on the Maximum Likelihood Approximate Nearest Neighbor Method}," Faculty of Computer Engineering, Amirkabir University of Technology, Tehran, Iran, Statistical Pattern Recognition Final Project Report, Jul. 2018.
	
	\textbf{A. Gholami}, "\textit{Implementation of A Naive Template Matching Algorithm with CUDA Technology}," Faculty of Computer Engineering, Amirkabir University of Technology, Tehran, Iran, Multu-core Programming Final Project Report, Apr. 2018.
	
	\textbf{A. Gholami}, "\textit{Linear Discriminant Functions, Support Vector
		Machine and Unsupervised Learning}," Faculty of Computer Engineering, Amirkabir University of Technology, Tehran, Iran, Statistical Pattern Recognition Coursework Report, Jun. 2018.
	
	\textbf{A. Gholami}, "\textit{Dimensionality reduction strategies; Principal
		Component Analysis, Fisher Linear Discriminant and Feature Subset
		Selection}," Faculty of Computer Engineering, Amirkabir University of Technology, Tehran, Iran, Statistical Pattern Recognition Coursework Report, Feb. 2018.
	
	\textbf{A. Gholami}, "\textit{Parametric and Non-parametric methods; Maximum Likelihood and 
		Bayesian Parameter Estimation and Kernel Density Estimation}," Faculty of Computer Engineering, Amirkabir University of Technology, Tehran, Iran, Statistical Pattern Recognition Coursework Report, Jan. 2018.
	
	\textbf{A. Gholami}, "\textit{Analysis of Bayesian Decision Boundaries, Risk
		Minimization and Bayes Error Bounds}," Faculty of Computer Engineering, Amirkabir University of Technology, Tehran, Iran, Statistical Pattern Recognition Coursework Report, Dec. 2017.
	
More available on \url{https://hexpheus.github.io/publications}.
	
\endinput