\documentclass[12pt]{article}
\usepackage{latexsym,amssymb,amsmath} % for \Box, \mathbb, split, etc.
% \usepackage[]{showkeys} % shows label names
\usepackage{cite} % sorts citation numbers appropriately
\usepackage{path}
\usepackage{url}
\usepackage{verbatim}
\usepackage[pdftex]{graphicx}

% horizontal margins: 1.0 + 6.5 + 1.0 = 8.5
\setlength{\oddsidemargin}{0.0in}
\setlength{\textwidth}{6.5in}
% vertical margins: 1.0 + 9.0 + 1.0 = 11.0
\setlength{\topmargin}{0.0in}
\setlength{\headheight}{12pt}
\setlength{\headsep}{13pt}
\setlength{\textheight}{625pt}
\setlength{\footskip}{24pt}

\renewcommand{\textfraction}{0.10}
\renewcommand{\topfraction}{0.85}
\renewcommand{\bottomfraction}{0.85}
\renewcommand{\floatpagefraction}{0.90}

\makeatletter
\setlength{\arraycolsep}{2\p@} % make spaces around "=" in eqnarray smaller
\makeatother

% change equation, table, figure numbers to be counted inside a section:
\numberwithin{equation}{section}
\numberwithin{table}{section}
\numberwithin{figure}{section}

% begin of personal macros
\newcommand{\half}{{\textstyle \frac{1}{2}}}
\newcommand{\eps}{\varepsilon}
\newcommand{\myth}{\vartheta}
\newcommand{\myphi}{\varphi}

\newcommand{\IN}{\mathbb{N}}
\newcommand{\IZ}{\mathbb{Z}}
\newcommand{\IQ}{\mathbb{Q}}
\newcommand{\IR}{\mathbb{R}}
\newcommand{\IC}{\mathbb{C}}
\newcommand{\Real}[1]{\mathrm{Re}\left({#1}\right)}
\newcommand{\Imag}[1]{\mathrm{Im}\left({#1}\right)}

\newcommand{\norm}[2]{\|{#1}\|_{{}_{#2}}}
\newcommand{\abs}[1]{\left|{#1}\right|}
\newcommand{\ip}[2]{\left\langle {#1}, {#2} \right\rangle}
\newcommand{\der}[2]{\frac{\partial {#1}}{\partial {#2}}}
\newcommand{\dder}[2]{\frac{\partial^2 {#1}}{\partial {#2}^2}}

\newcommand{\nn}{\mathbf{n}}
\newcommand{\xx}{\mathbf{x}}
\newcommand{\uu}{\mathbf{u}}
\usepackage{tikz}
\usetikzlibrary{arrows}
\usetikzlibrary{positioning}
\usepackage{titlesec}
\newcommand{\junk}[1]{{}}
\usepackage{xcolor}
\definecolor{darkblue}{rgb}{0,0,0.4}
\usepackage[colorlinks = true,
linkcolor = darkblue,
urlcolor  = darkblue,
citecolor = darkblue,
anchorcolor = darkblue]{hyperref}
% set two lengths for the includegraphics commands used to import the plots:
\newlength{\fwtwo} \setlength{\fwtwo}{0.45\textwidth}
% end of personal macros

\begin{document}
\DeclareGraphicsExtensions{.jpg}

\begin{center}
\textsc{\Large Research \& Technical Presentation} \\[2pt]
	\textsc{\large Assignment 2}\\
	\vspace{0.5cm}
  Ali Gholami \\[6pt]
  Department of Computer Engineering \& Information Technology\\
  Amirkabir University of Technology  \\[6pt]
  \def\UrlFont{\em}
  \url{http://ceit.aut.ac.ir/~aligholamee}\\
    \href{mailto:aghce@aut.ac.ir}{\textit{aghce@aut.ac.ir}}
\end{center}

\begin{abstract}
This assignment reviews the different types of research. We'll give an example for each type of research. We'll also study the usage of \textit{fish-bone} diagram as a conceptual framework. We'll focus on the \textit{mind-map} and draw that for a particular point.
\end{abstract}

\subparagraph{Assignment 2 key words.} \textit{Theoretical Research, Practical Research, Incremental Research, Conceptual Framework, Mind Map, Computer Engineering, Software Engineering.}
\section{Practical Problems}
\subsection{1. An Illustration of Research in Computer Engineering}

Provide examples for the different methods of research in computer engineering. These examples must cover all types of research in computer engineering including:
\textit{\textbf{Theoretical} Research, \textbf{Practical} Research and \textbf{Incremental} Research.} 

\subsection{Solution}

Firstly, we'll review the different methods of research in science \& engineering. Then we'll exemplify each. 

\begin{itemize}
	\item{\textbf{Theoretical Research}} -- In this type of research, the whole effort is made to expand the borders of pure science. Its important to mention that the focus is neither on the application of this science nor the quality of human life. The goal of this type of research is to provide the fundamentals of pure science.
	\item{\textbf{Practical Research}} -- This type of research will make use of the explained \textit{Theoretical Research} to improve the quality of human life. It also provides solutions to the existing complications. The goal of this type of research is to apply the science on the day-to-day life problems.
	\item{\textbf{Incremental Research}} -- Incremental research looks for the usage of above techniques to implement them as a real-life product. The focus is to make use of the two mentioned techniques in the industries.
\end{itemize}

Some of the best examples of each of these research techniques are provided in the table 1.1. These examples are the results of my investigation through the \textit{Google Scholar} and other references that are available in the final column.

\begin{table} \centering
	\begin{tabular}{rcccc}
		\hline
		$ Type \ of \ Research $ &
		$ Example $ & $ Reference $ \\
		\hline
		Theoretical & Request for authorization & ATM \\
		Theoretical & Repeat authorization request & ATM\\
		Theoretical & Respond to authorization request & Central Computer\\
		Theoretical & Request for fund & ATM \\
		Practical & Repeat fund request & ATM \\
		Practical & Respond to financial request & Central Computer \\
		Practical & Request for account report & ATM \\
		Practical & Respond to account report & Central Computer \\
		Incremental & Reverse a card-to-card transaction & ATM \\
		Incremental & Rollback a card-to-card transaction & ATM \\
		Incremental & Request for public announcement due date & ATM \\
		Incremental & Respond to the public announcement & Central Computer \\
				
		\hline
	\end{tabular}
	\caption{Demonstration of proposed examples of different research types.}
	\label{tabconvdemo}
\end{table}

\begin{enumerate}
	\item{Authorization Message}
		\begin{itemize}
			\item{Authorize the card pass phrase}
			\item{Determine if funds are available}
			\item{Determine if the destination card exists in a card-to-card transaction}
		\end{itemize}
		
	\item{Financial Message}
		\begin{itemize}
			\item{Post funds to the accounts in card-to-card transactions}
			\item{Post funds to the accounts in \textit{POS} transactions}
			\item{Fund posting approvals}
		\end{itemize}
	
	\item{Reversal \& Rollback Message}
		\begin{itemize}
			\item{Reverse the previous authorization action}
			\item{Rollback the previous financial message}
		\end{itemize}
		
	\item{Administrative Message}
		\begin{itemize}
			\item{Transmit the administrative messages and advices}
			\item{Public announcements on the \textit{ATM}}
		\end{itemize}
		
	\item{Network Management Message}
		\begin{itemize}
			\item{Secure key exchange}
		\end{itemize}
	
\end{enumerate}



A complete example of a fund request is described in the figure 1.2. \textbf{Firstly}, the \textit{ATM} sends an authorization request to the central computer. \textbf{Secondly}, The central computer responds to the incoming request. \textbf{Thirdly}, in case the authorization is successful, a fund request is sent to the central computer. \textbf{Fourthly}, the fund request is validated and the reponse is sent to the \textit{ATM}. In the situation, the user might ask for a reversal. If that happens, the reversal requests/responses are transferred.

\begin{figure}[!h]
	\centering
		\begin{tikzpicture}[scale=1]
		\tikzstyle{ann} = [draw=none,fill=none,right]
		\matrix[nodes={draw, ultra thick, fill=blue!10},
		row sep=1.5cm,column sep=2cm] {
			\node[rectangle] (a1) {ATM - Request for authentication}; &
			\node[rectangle] (c1) {Computer - Authentication reponse};\\
			\node[rectangle] (a2) {ATM - Request for fund}; &
			\node[rectangle] (c2) {Computer - Fund reponse};\\
			\node[rectangle] (a3) {ATM - Request for account report}; &
			\node[rectangle] (c3) {Computer - Account report reponse};\\
		};
		
			\draw [->] [line width=2pt, -stealth](a1) to [bend left=15] node{} (c1);
			\draw [->] [line width=2pt, -stealth](c1) to [bend left=15] node{} (a1);
			
			\draw [->] [line width=2pt, -stealth](a2) to [bend left=15] node{} (c2);
			\draw [->] [line width=2pt, -stealth](c2) to [bend left=15] node{} (a2);

			\draw [->] [line width=2pt, -stealth](a3) to [bend left=15] node{} (c3);
			\draw [->] [line width=2pt, -stealth](c3) to [bend left=15] node{} (a3);

		\end{tikzpicture}
		
		\caption{A complete fund request flow diagram.}
		\label{tabconvdemo}
\end{figure}

Please refer to the beginning of this solution for the assumptions about the \textit{transport} layer.

\titleformat{\section}
{\normalfont\Large\bfseries}   % The style of the section title
{}                             % a prefix
{0pt}                          % How much space exists between the prefix and the title
{Section \thesection:\quad}    % How the section is represented

\subsection{2. HFC \& Collision in Downstream}
Given an \textit{HFC} communication medium, find out whether the transmission rate is \textit{dedicated} to one user or it is shared among users in the network. Is it possible for a downstream in an \textit{HFC} channel to have collision? Describe your answer.

\subsection{Solution}

As the description for the \textit{HFC(Hybrid fiber-coaxial)} medium specifies, the combination of both \textit{optical fiber} and \textit{coaxial cable} is used in a broadband network. As an example for the functionality of this medium, the television channels are sent from the cable system's distribution facility, the \textit{\textbf{headend}}, to local communities through optical fiber subscriber lines. At the local community, a box called an \textit{optical node} translates the signal from a light beam to electrical signal, and sends it over coaxial cable lines for distribution to subscriber residences.\\
\subparagraph{HFC Transmission Rate }HFC bandwidth is shared among users. So, each user on a tail-end of the coaxial cable can use the same transmission rate as others.\\
\subparagraph{Collision in Downstream}

The downstream channel, provides the data from a single source called head-end. Then the data is distributed among the residences. Thus, there are no collisions in the downstream channel.
\\


\subsection{3. Dial-up, ADSL, FTTH, HFC Modems}
The modems titled here are widely used as a home-access to the Internet. Provide an example of \textit{maximum transmission rate}. Describe whether these rates are shared or not.

\subsection{Solution}

Table 1.2 provides various \textit{transmission rates(Bitrate)} for each of these modems.

\begin{table}[!h]
	\centering
	\begin{tabular}{rcccc}
		\hline
		$ Modem $ &
		$ Bitrate $ & $ Usage $ \\
		\hline
		Dial-up & 33.6(kbit/s) -- 48(kbit/s) -- 56(kbit/s) & Unshared \\
		ADSL & 8.0(Mbit/s) -- 12.0(Mbit/s) -- 24(Mbit/s) & Unshared -- Shared\\
		HFC &  100(Mbit/s) & Shared\\
		FTTH & 1(Gbit/s)(Google Fiber) & Unshared(one single home)\\
		\hline
	\end{tabular}
	\caption{Bitrate samples for different types of modems.}
	\label{tabconvdemo}
\end{table}

\end{document}