%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{multicol}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://sourabhbajaj.com/}{\Large Ali Gholami}} & Email : \href{mailto:aligholamee@outlook.com}{aligholamee@outlook.com}\\
  \href{https://aligholamee.github.io}{https://aligholamee.github.io} & Mobile : +98-939-619-1804 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Amirkabir University of Technology}{Tehran, IR}
      {Bachelor of Science in Software Engineering;  \textbf{GPA: 17.55/20}}{Aug 2014 -- Dec 2018}
    \resumeSubheading
      {Kamal High-school}{Tehran, IR}
      {Diploma in Physics and Mathematics;  \textbf{GPA: 19/20}}{Aug 2012 -- Jan 2014}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Research Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Bio-intelligence Center, Sharif University of Technology}{Tehran, IR}
      {Research Assistant, Advisors: Prof. Ali Ghazizadeh and Prof. Reza Lashgari}{Jul. 2018 - Present}
      \resumeItemListStart
        \resumeItem{Bio-medical Image Analysis}
          {Development of image processing algorithms and deep learning architectures to extract the sarcoidosis patterns in medical lung scans.}
      \resumeItemListEnd
      
    \resumeSubheading
    {Machine Learning Lab, Amirkabir University of Technology}{Tehran, IR}
    {Freelance Researcher, Advisors: Prof. Mohammad Rahmati and Prof. Mahmoud Momtazpour}{Nov. 2017 - Jul. 2018}
    \resumeItemListStart
    \resumeItem{Visual Question Answering \& Image Captioning}
    {Explored state of the art \textit{CNN} and \textit{RNN} architectures in the task of \textit{VQA} and \textit{IC}.}
    \resumeItem{Statistical Face Recognition}
    {Developed a real-time face recognition system with \textit{Tensorflow} and \textit{OpenCV} frameworks which implemented the maximum likelihood approximate nearest neighbor method for rapid selection of the reference images in large-scale databases.}
    \resumeItem{Image Template Matching with CUDA}
    {Designed and implemented a fast naive image template matching algorithm confirming the best practices in parallel processing using \textit{CUDA} technology.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Work Experience}
\resumeSubHeadingListStart

\resumeSubheading
{ArvanCloud}{Tehran, IR}
{Web Development Intern}{Jun. 2017 - Sep. 2017}
\resumeItemListStart
	\resumeItem{Smart Lock System}
	{Developed an administrative panel for an smart lock project using \textit{PHP} and \textit{Laravel}.}
	\resumeItem{Coding Practices}
	{Practiced the best coding styles in Javascript, especially Node.js and React.js.}
\resumeItemListEnd

\resumeSubheading
{Fandogh}{Tehran, IR}
{Mobile Development Intern}{Jun. 2017 - Sep. 2017}
\resumeItemListStart
\resumeItem{Toofan Weather}
{Designed and implemented a weather forecast application with \textit{Java SE} and \textit{Android Studio}.}
\resumeItem{Ranjoor Poetry}
{Developed a poetry application with \textit{React Native}.}
\resumeItemListEnd



\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Teaching Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Microprocessors and Assembly Language}{Tehran, IR}
{Supervisor: Prof. Mohammad Mehdi Homayounpour}{Sep. 2017 - Dec. 2017}

\resumeSubheading
{Foundations of Programming}{Tehran, IR}
{Supervisor: Prof. Azadeh Mansouri}{Sep. 2015 - Dec. 2015}


\resumeSubHeadingListEnd


%
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Languages}{: \textit{Python, C/C++, Java SE, VHDL, ARM Assembly, AVR Assembly, Racket, ML, Scheme, HTML/CSS, Javascript, Latex.}}
     \hfill
   }
   \item{
   	\textbf{Frameworks and Environments}{: \textit{Tensorflow, Numpy, Matplotlib, Pandas, RapidMiner, Weka, OpenMP, CUDA, React Native, Node.js, Laravel.}}
   	\hfill
   }
   \item{
   	\textbf{Databases}{: \textit{MongoDB, MySQL, PostgreSQL.}}
   	\hfill
   }
 \resumeSubHeadingListEnd


%-------------------------------------------

%-----------EXPERIENCE-----------------
\section{Selected Honors}
 \resumeSubHeadingListStart
 \vspace{0.1cm}
  \item{
  	\textbf{Full Admission} to 
  	\textbf{Amirkabir University of Technology}
  	due to outstanding\hfill {Aug. 2018}\\ performance at Kharazmi University of Tehran and Amirkabir University of Technology.
  }
 
 \item{
	\textbf{Ranked top 3} among most active \textbf{GitHub} developers in Iran.\hfill{Jun. 2018}
 }
 \item{
	\textbf{Member of Executive Team}
	at the 17'th \href{https://icpc.baylor.edu/regionals/finder/tehran-2017}{International Collegiate} \hfill {Nov. 2017}\\  \href{https://icpc.baylor.edu/regionals/finder/tehran-2017}{Programming Contest} held at the \href{http://ceit.aut.ac.ir}{Amirkabir University of Technology}.

 }
 
 \item{
	\textbf{Ranked top 3}
	among all bachelor students at Computer Engieering \hfill {Jul. 2016}\\ Department, \href{http://khu.ac.ir}{Kharazmi University of Tehran}.
 }
 
 \item{
 	\textbf{Ranked top 0.6\%}
 	in the \textbf{Nationwide} University Entrance Exam \hfill {Jul. 2014}\\ among all students (approximately \textbf{250,000}) in 
 	mathematics and physics.
 		
 }
 
 \item{
	\textbf{ٍElected}
	as the \textbf{tidiest} student at the campus of international \hfill {Aug. 2011}\\ summer school, \textit{\href{https://www.monterosa.ch/}{Institute Monte Rosa}}, Montreux, \textbf{Switzerland}. 
 	
 }
 \resumeSubHeadingListEnd
	

\section{Selected Courses}
\begin{center}
	\renewcommand{\arraystretch}{1}
	\setlength{\tabcolsep}{40pt}
	\begin{tabular}{ c c }
		\textbf{Statistical Pattern Recognition}: \hfill{18/20} & \textbf{Machine Learning}: \hfill{19.5/20} \\ 
		\textbf{Foundations of Data Mining}: \hfill{18.7/20} & \textbf{Database Design}: \hfill{20/20} \\  
		\textbf{Data Structures}: \hfill{18.5/20} &\textbf {Algorithm Design}: \hfill{19.31/20}\\
		\textbf{Engineering Statistics}: \hfill{18.5/20} & \textbf{Engineering Mathematics}: \hfill{19/20}
	\end{tabular}
\end{center}

\section{Selected Technical Reports}

 \resumeSubHeadingListStart
 \vspace{0.1cm}
   \item{
   	A. Gholami, "\textbf{Linear Discriminant Functions, Support Vector
   	Machine and Unsupervised Learning}," Faculty of Computer Engineering, Amirkabir University of Technology, Tehran, Iran, Statistical Pattern Recognition Coursework Report, Jun. 2018.
   }
   
  \item{
  	A. Gholami, "\textbf{Dimensionality reduction strategies; Principal
  	Component Analysis, Fisher Linear Discriminant and Feature Subset
  	Selection}," Faculty of Computer Engineering, Amirkabir University of Technology, Tehran, Iran, Statistical Pattern Recognition Coursework Report, Feb. 2018.
  	
  }
    
        \item{
        	A. Gholami, "\textbf{Parametric and Non-parametric methods; Maximum Likelihood and 
        	Bayesian Parameter Estimation and Kernel Density Estimation}," Faculty of Computer Engineering, Amirkabir University of Technology, Tehran, Iran, Statistical Pattern Recognition Coursework Report, Jan. 2018.
        }
        
        \item{
        	A. Gholami, "\textbf{Analysis of Bayesian Decision Boundaries, Risk
        	Minimization and Bayes Error Bounds}," Faculty of Computer Engineering, Amirkabir University of Technology, Tehran, Iran, Statistical Pattern Recognition Coursework Report, Dec. 2017.
        }
 
	 \item{More available on \url{https://aligholamee.github.io/publications}}
  \resumeSubHeadingListEnd
  
 \section{Referees}
\resumeSubHeadingListStart

\resumeSubheading
{Prof. Mohammad Rahmati}{\textit{Email: rahmati@aut.ac.ir}}
{Faculty of Computer Engineering, Amirkabir University of Technology}{Phone: +98 (21) 64542741}

\resumeSubheading
{Prof. Mohammad Mehdi Homayounpour}{\textit{Email: homayoun@aut.ac.ir}}
{Faculty of Computer Engineering, Amirkabir University of Technology}{Phone: +98 (21) 64542722}

\resumeSubheading
{Prof. Mahmoud Momtazpour}{\textit{Email: momtazpour@aut.ac.ir}}
{Faculty of Computer Engineering, Amirkabir University of Technology}{Phone: +98 (21) 64542721}

\resumeSubHeadingListEnd

\end{document}

\grid
